Interval Probability for Fuzzy Quantum Theories

### 2016-05-21 prob.tex
prob.tex \section{Quantum Probability Spaces} before send the email...

\begin{definition}[Projection Operators;
Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal, 
where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when there is no ambiguity. 
\item Conversely, every projection~$P$ can be expressed as
$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\qed\end{definition}

@@

is also a projection operator, called complement. It is orthogonal to $P$, has

@@

\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.

@@

$P_{1}$ and $P_{2}$ are independent if $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.

@@

\yutsung{\begin{example}[Independence of product state] Consider
the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
with the following projections:
\[
\begin{array}{rcl}
P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
\]
and their probabilities: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
\]
On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
we have
\begin{eqnarray*}
\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
\end{eqnarray*}
Therefore, $P_{1}$ and $P_{3}$ commute, but not independent. On
the other hand, $P_{1}$ also commutes with $P_{2}$, and
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
\end{eqnarray*}
so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}

\begin{example}[Independence of any states] In general, for any orthonormal
basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{3}$, we can always
pick 
\[
\begin{array}{rcl}
P_{1}=\proj{\psi_{0}}+\proj{\psi_{1}},\quad P_{2}=\proj{\psi_{0}}+\proj{\psi_{2}},\quad P_{3}=\proj{\psi_{0}}\textrm{ .}\end{array}
\]
With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
where $\ket{\psi}=\frac{1}{2}\sum_{j=0}^{3}\ket{\psi_{j}}$, their
probabilities are
\[
\begin{array}{rcl}
\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/4\textrm{ ,}\end{array}
\]
and we have
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{3}\right)=\mu\left(P_{1}P_{2}\right)\textrm{ .}
\end{eqnarray*}
In particular, the following four Bell states form an orthonormal
basis~\cite{CabelloPRL.86.2001}, 
\begin{eqnarray*}
\ket{\phi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right)\textrm{ ,}\\
\ket{\psi^{\pm}} & = & \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
\end{eqnarray*}
Their sum is also a Bell state~
\[
\ket{\psi}=\frac{1}{2}\left(\ket{\phi^{+}}+\ket{\phi^{-}}+\ket{\psi^{+}}+\ket{\psi^{-}}\right)=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{01}\right)\textrm{ .}
\]
With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
$\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
are independent as we expect.\qed\end{example}

The definition of independence is interesting, and we definitely need
to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
theorem. However, the definition diverges, and our definition didn't come from
any sources directly. We may need to check more papers to find a source or
adopt one of the majority definition (if there is one)...}

>>>>

\begin{definition}[Projection Operators;
Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal, 
where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when there is no ambiguity. 
\item Conversely, every projection~$P$ can be expressed as
$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\qed\end{definition}

@@

is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has

@@

\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.

@@

$P_{1}$ and $P_{2}$ are \emph{independent} if
$\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.

@@

\yutsung{\begin{example}[Independence of product state] Consider
the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
with the following projections:
\[
\begin{array}{rcl}
P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
\]
and their probabilities: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
\]
On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
we have
\begin{eqnarray*}
\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
\end{eqnarray*}
Therefore, $P_{1}$ and $P_{3}$ commute, but are not independent. On
the other hand, $P_{1}$ also commutes with $P_{2}$, and
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
\end{eqnarray*}
so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}

\begin{example}[Independence of any states] In general, for any orthonormal
basis~$\left\{ \ket{\psi_{j}}\right\} _{j=0}^{3}$, we can always
pick 
\[
\begin{array}{rcl}
P_{1}=\proj{\psi_{0}}+\proj{\psi_{1}},\quad P_{2}=\proj{\psi_{0}}+\proj{\psi_{2}},\quad P_{3}=\proj{\psi_{0}}\textrm{ .}\end{array}
\]
With the probability measure~$\mu\left(P\right)=\melement{\psi}{P}$,
where $\ket{\psi}=\frac{1}{2}\sum_{j=0}^{3}\ket{\psi_{j}}$, their
probabilities are
\[
\begin{array}{rcl}
\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/4\textrm{ ,}\end{array}
\]
and we have
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{3}\right)=\mu\left(P_{1}P_{2}\right)\textrm{ .}
\end{eqnarray*}
In particular, the following four Bell states form an orthonormal
basis~\cite{CabelloPRL.86.2001}: 
\[
\ket{\phi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{00}\pm\ket{11}\right),\quad
\ket{\psi^{\pm}} = \frac{1}{\sqrt{2}}\left(\ket{01}\pm\ket{10}\right)\textrm{ .}
\]
Their sum is also a Bell state~
\[
\ket{\psi}=\frac{1}{2}\left(\ket{\phi^{+}}+\ket{\phi^{-}}+\ket{\psi^{+}}+\ket{\psi^{-}}\right)=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{01}\right)\textrm{ .}
\]
We know $\proj{\phi^{+}}+\proj{\psi^{+}}$ and $\proj{\phi^{+}}+\proj{\psi^{-}}$
are independent projections with respect to the probability
measure~$\mu\left(P\right)=\melement{\psi}{P}$.\qed\end{example}

The definition of independence is interesting, and we definitely need
to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
theorem. However, the definition diverges, and I haven't found any source to
support our definition, yet. We may need to check more papers to find a source
to support our definition or to find the majority definition (if there is one)...}
